---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# powers

This package is for a homework assignment. It is not meant to be serious!  
It provides a few functions for dealing with powers.

## Installation

```{r}
# install.packages("devtools")
devtools::install_github("rainerlempert/Lempert_Rainer_hw09")

library(powers)

#>   Use `force = TRUE` to force installation
```


## Functions

Here are the functions included in the package:

- `square` - squares a vector, logical, or number  
- `cube` - cubes a vector, logical, or number  
- `pow` - takes the power of a vector, logical, or number  
- `boxcox` - takes the boxcox transformation of vector, logical, or number, given a lambda 


## Examples

Look to the vignette for more thorough examples what this can do

```{r}
square(3)
boxcox(1:10, 4)
```
